Your Paper Title

### 2025-05-16 Master Thesis/thesis.tex
New

First, let us consider the most general case. We need to introduce n complex-valued vectors $r_i^\mu$ subject to 
\begin{itemize}
    \item $\sum_{i=1}^{n}r_i^\mu=0$,
    \item $r_i\cdot r_j=0$ for all $i,j=1,2,\cdots ,n$. In particular, $r_i^2=0$,
    \item $p_i\cdot r_i=0$ for each i(no sum).
\end{itemize}
These vectors $r_i$ are used to define n shifted momentum
\begin{equation}
    \hat{p}_i^\mu\equiv p_i^\mu+zr_i^\mu\quad \text{with}\quad z\in \mathcal{C}
\end{equation}
Note that, by imposing these constraints,
\begin{itemize}
    \item Momentum conservation holds for the shifted momentum: $\sum_{i=1}^{n}\hat{p}_i^\mu=0$,
    \item We have $\hat{p}_i^2=0$, so each shifted momentum still keep on-shell
    \item For a non-trival \footnote{non-trival here means at least two and no more than n-2 such that $P_I^2\neq 0$} subset of momentum $\{p_i\}_{i\in I}$,
    define $P_i^\mu=\sum_{i\in I}p_i^\mu$. Then $\hat{P}_I^2$ is \textbf{linear} in z:
    \begin{equation}
        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I)
    \end{equation}
    beacuse the $z^2$ term vanishes. We can write 
    \begin{equation}
        \hat{P}_I^2=-\frac{P_I^2}{z_I}(z-z_I)\quad \text\quad {with} z_I=\frac{P_I^2}{2P_I\cdot k}
        \label{2.63}
    \end{equation}
\end{itemize}
If we consider the original amplitude $A_n$ in terms of the shifted momentum $\hat{p}_i^\mu$ instead of original momentum. Then the amplitude can be seen as 
a holomorphic function of z. Actually, if we set $z=0$, we can obtain the origin ampltide $A_n=\hat{A}_n(z=0)$.

@@

Here, we need to notice that in 6-point case, we will first meet the NMHV amplitudes like $A_6[1,2,3^+,4^+,5^-,6^-]$. Although we can still compute it by samely utlizing BCFW recursion relaiton, but it is quite messy. 
\subsubsection{n-point case}
It is not so hard to generallize these results to general case, here we only provide the compact formula, and the negligible sign are neglected
\begin{equation*}
    A[1,2,\cdots,n^-]=\frac{\avg{1n}^2\avg{2n}^2}{\mdavg{12}{23}\cdots\mdavg{n-1,1}{n,1}}
\end{equation*} 
\subsection{Pure 2-site sector}
\subsubsection{4-point case}
The color structure for this kind of amplitude has special form, like
\begin{equation}
    (T_1^{a_1}T_1^{a_2}\cdots T_1^{a_{n_1}})_{ij}(T_2^{b_1}T_2^{b_2}\cdots T_2^{b_{n_2}})_{\bar{j}\bar{i}}
\end{equation}
Here we start from the 4-point case with the color factor
\begin{equation}
    (T_1^a)_{ij}(T_2^b)_{\bar{j}\bar{i}}
\end{equation}
It is more straightforward to observe the color structure in terms of double line notation as follows 
\vspace{0.5em}

@@

Only two diagrams have semmingly non-zero contribution,

@@

    \includegraphics{6pt.eps}
    \caption{6pt.}
    \label{5}

@@

so the full color ordered amplitude equals to
    A_1&=\frac{(-1)\asqu{\hat{2}6}\asqu{16}}{\mdavg{25}{56}\!\avg{61}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
    &=\frac{\asqu{26}\avg{16}}{\mdavg{25}{56}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[34]^3}{[4\hat{I}][\hat{I}3]}\notag\\
    &=\frac{\asqu{26}\avg{16}\bcancel{[34]^3}\bcancel{\avg{42}}}{\mdavg{25}{56}\!\mdavg{41}{32}\!\avg{43}\bcancel{[43][43][34]}\bcancel{\avg{24}}}\notag\\
    &=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
where we have used the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the following identities
    \cbrak{2\hat{I}}{\hat{I}3}=\cbrak{24}{43}, \qquad \acbrak{4\hat{I}}{\hat{I}1}=\acbrak{43}{\hat{3}1}
The point here is that we first $\avg{\hat{3}1}$ which does not appear in 5-point case, so we nned to compute it carefully
    \text{pole position}: \quad \hat{P_{34}}^2=0=2P_3\cdot P_4=\cbrak{4\hat{3}}{34}\qquad\Rightarrow \qquad \avg{4\hat{3}}=0\notag\\
    \avg{43}+z\avg{42}=0\qquad \Rightarrow \qquad z=-\frac{43}{42}
then
    \avg{\hat{3}1}=\avg{31}+z\avg{21}&=\avg{31}-\frac{\avg{43}}{\avg{42}}\avg{21}\notag\\
    &=\frac{\mdavg{42}{31}-\mdavg{43}{21}}{42}\notag\\
    &=\frac{\mdavg{41}{32}}{\avg{42}}
where we have used the Fierz identity
    \mdavg{42}{31}+\mdavg{41}{23}+\mdavg{43}{12}=0.
Simiraly, we can compute the second diagram
    A_2=\frac{[\hat{2}5][5\hat{I}]}{[\hat{I}\hat{2}]}\times\frac{1}{s_{25}}\times \frac{(-1)\asqu{16}\asqu{\hat{I}6}}{\mdavg{\hat{I}\hat{3}}{\hat{3}4}
    \!\mdavg{41}{\hat{I}6}\!\avg{61}}
but from the pole position
    \hat{P_{25}}^2=0=2P_2\cdot P_5=\cbrak{52}{\hat{2}5}\qquad\Rightarrow \qquad [\hat{2}5]=0,
and simiraly
    [\hat{2}\hat{I}]=[5\hat{I}]=0.
Then we can conclude that the left part of the amplitude equals to 0 so $A_2=0$. Finally, we obtain the color-ordered amplitude 
    A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=A_1+A_2=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}.
\subsection{n-point case}
Here, we first propose a compact formula for the color-ordered amplitude
    A=\frac{\asqu{2a}\!\asqu{1a}}{\underbrace{\avg{2\star}\cdots \avg{\star 1}}_{SU(N_1)}\underbrace{\avg{2\ast }\cdots \avg{\ast 1}}_{SU(N_2)}}
where a refer to the particle with - helicity, whichever gauge group it belongs to. And, `$\star$' refers to the ordering for the first gauge group, `$\ast$'
refers to the ordering for the second gauge group. We suppose there are $n_1$ gauge boson 1, $n_2$ gauge boson 2, so the n-point means that $n=n_1+n_2+2$.
The usual way to prove this kind of compact formula is induction. First we suppose that all of the amplitudes with external point lower than n satisfy the compact formula.

>>>>

First, let us consider the most general case. We need to introduce n complex-valued vectors $r_i^\mu$ subject to 
\begin{itemize}
    \item $\sum_{i=1}^{n}r_i^\mu=0$,
    \item $r_i\cdot r_j=0$ for all $i,j=1,2,\cdots ,n$. In particular, $r_i^2=0$,
    \item $p_i\cdot r_i=0$ for each i(no sum).
\end{itemize}
These vectors $r_i$ are used to define n shifted momentum
\begin{equation}
    \hat{p}_i^\mu\equiv p_i^\mu+zr_i^\mu\quad \text{with}\quad z\in \mathcal{C}
    \label{2.61}
\end{equation}
Note that, by imposing these constraints,
\begin{itemize}
    \item Momentum conservation holds for the shifted momentum: $\sum_{i=1}^{n}\hat{p}_i^\mu=0$,
    \item We have $\hat{p}_i^2=0$, so each shifted momentum still keep on-shell
    \item For a non-trival \footnote{non-trival here means at least two and no more than n-2 such that $P_I^2\neq 0$} subset of momentum $\{p_i\}_{i\in I}$,
    define $P_i^\mu=\sum_{i\in I}p_i^\mu$. Then $\hat{P}_I^2$ is \textbf{linear} in z:
    \begin{equation}
        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I)
    \end{equation}
    beacuse the $z^2$ term vanishes. We can write 
    \begin{equation}
        \hat{P}_I^2=-\frac{P_I^2}{z_I}(z-z_I)\quad \text\quad {with} z_I=\frac{P_I^2}{2P_I\cdot k}
        \label{2.63}
    \end{equation}
\end{itemize}
If we consider the original amplitude $A_n$ in terms of the shifted momentum $\hat{p}_i^\mu$ instead of original momentum. Then the amplitude can be seen as 
a holomorphic function of z. Actually, if we set $z=0$, we can obtain the origin ampltide $A_n=\hat{A}_n(z=0)$.

@@

Here, we need to notice that in 6-point case, we will first meet the NMHV amplitudes like $A_6[1,2,3^+,4^+,5^-,6^-]$. Although we can still compute it by samely utlizing BCFW recursion relaiton, but it is quite messy. So it is better to introduce another method named CSW expansion.

We introduce the general shift in section 2.4.1 like \eqref{2.61} and specialize to BCFW shift in section 2.4.2 like \eqref{2.71}. Here, I will introduce another kind of recursion relation. Consider a shift which is implemented by a ``holomorphic'' square spinor shift:
\begin{equation}
    \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{i}=\aket{i},
    \label{4.37}
\end{equation}
Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n}c_i\aket{i}=0$. Notice that this equation can be always solved and the shift spinors also satisfy momentum conservation and on-shell condition.

We consider here a situation where all $c_i \neq 0$ so that all momentum lines are shifted via\eqref{4.37} – this is an all-line shift. And the large - z behavior of all-line shift can be found in this paper\cite{Cohen:2010mi}.
As shown in \cite{Elvang:2008vz}, N$^{K}$MHV gluon tree amplitudes fall off as $1/z^K$ under an all-line shift in the large-$z$ limit. This implies that all tree-level gluon amplitudes---except the MHV case with $K = 0$---can be fully constructed using the all-line shift recursion relations.

The critical point here is that the MHV amplitudes depend only on angle spinors, so the only way we can know about the square-spinor
shift is arrording to the internal line angle spinors $\aket{\hat{P}_I}$, and this $\aket{\hat{P}_I}$ can be written in a wise manner
\begin{equation}
    \aket{\hat{P}_I}\frac{[\hat{P}_I X]}{[\hat{P}_I X]}=\hat{P}_I\sket{X}\frac{1}{[\hat{P}_IX]}=P_I\sket{X}\frac{1}{[\hat{P}_IX]},
\end{equation}
where we can drop the hat upon the shifted momentum $\hat{P}_I$ because the shift is proportional to $\sket{X}$, so that it will become 0 when contracting with itself. And other point is there are same number of $\aket{P}_I$ appearing in the numerator and demoninator as there's no helicity dependence on internal propagator, so that all of $\frac{1}{[\hat{P}_IX]}$ can be canceled with other.

Then for each diagram we can use the following prescription
\begin{equation}
    \aket{P}_I \quad \rightarrow \quad P_I\sket{X}, 
\end{equation}

For example
\begin{equation}
    \raisebox{-5.5mm}{\includegraphics[height=1.5cm]{csw-6pt-A2}}
   ~=~ 
\frac{\langle 1|P_{156}|X]^4}{\langle 1|P_{156}|X]\langle 5|P_{156}|X]\langle 56\rangle \langle 61\rangle}
\cdot \frac{1}{P_{156}^2}
\cdot \frac{\langle 23\rangle^4}{\langle 23\rangle \langle 34\rangle \langle 4|P_{156}|X]\langle 2|P_{156}|X]}
\end{equation}

In general, individual diagrams exhibit an explicit dependence on the reference spinor $\sket{X}$. However, the full tree-level amplitude must remain independent of this arbitrary choice.The expansion of amplitudes using MHV vertex diagrams extends naturally beyond the NMHV level. More generally, an N$^K$MHV tree-level amplitude can be expressed as a sum over all tree diagrams containing exactly $K + 1$ MHV vertices.
Henceforth, this method is called \tif{MHV vertex expansion}. But actually, this method was discovered by Cachazo, Svrcek, and Witten \cite{Cachazo:2004kj} befor introducing complex shift, so it is also named \tif{CSW expansion}. 
\subsubsection{n-point case}
It is not so hard to generallize these results to general case, here we only provide the compact formula, and the negligible sign are neglected
\begin{equation*}
    A[1,2,\cdots,n^-]=\frac{\avg{1n}^2\avg{2n}^2}{\mdavg{12}{23}\cdots\mdavg{n-1,1}{n,1}}
\end{equation*} 
\subsection{Pure 2-site sector}
\subsubsection{4-point case}
The color structure for this kind of amplitude has special form, like
\begin{equation}
    (T_1^{a_1}T_1^{a_2}\cdots T_1^{a_{n_1}})_{ij}(T_2^{b_1}T_2^{b_2}\cdots T_2^{b_{n_2}})_{\bar{j}\bar{i}}
\end{equation}
Here we start from the 4-point case with the color factor
\begin{equation}
    (T_1^a)_{ij}(T_2^b)_{\bar{j}\bar{i}}
\end{equation}
It is more straightforward to observe the color structure in terms of double line notation as follows 
\vspace{0.5em}

@@

Evey OPP corresponds different BCFW diagrams, here for concreteness, we list all of the diagrams as following 
\begin{itemize}
    \item $(3_1^+,4_1^+,5_2^+,6_2^-)$

@@

        \includegraphics{6pt1_1.pdf}
        \caption{Order $(3_1^+,4_1^+,5_2^+,6_2^-)$}

@@

    \item $(3_1^+,5_2^+,4_1^+,6_2^-)$
        \includegraphics{6pt1_2.pdf}
        \caption{Order $(3_1^+,5_2^+,4_1^+,6_2^-$}
    \item $(3_1^+,5_2^+,6_2^-,4_1^+)$
        \includegraphics{6pt1_3.pdf}
        \caption{Order $(3_1^+,5_2^+,6_2^-,4_1^+)$}
    \item $(5_2^+,3_1^+,4_1^+,6_2^-)$
        \includegraphics{6pt1_4_1.pdf}
        \includegraphics{6pt_1_4_2.pdf}
        \caption{Order $(5_2^+,3_1^+,4_1^+,6_2^-)$}
    \item $(5_2^+,3_1^+,6_2^-,4_1^+)$
        \includegraphics{6pt1_5_1.pdf}
        \includegraphics{6pt1_5_2.pdf}
        \caption{Oredr $(5_2^+,3_1^+,6_2^-,4_1^+)$}
    \item $(5_2^+,6_2^-,3_1^+,4_1^+)$
        \includegraphics{6pt_1_6_1.pdf}
        \includegraphics{6pt_1_6_2.pdf}
        \includegraphics{6pt_1_6_3.pdf}
        \caption{Order $(5_2^+,6_2^-,3_1^+,4_1^+)$}
\end{itemize}

Most of them equal to 0 because of there are no interaction between two gauge bosons or special helicity configuration. And some of the nonvanishing diagrams have same structure under OPP so they conly contribute once. Finally, only two diagrams have semmingly non-zero contribution,
\par
\begin{figure}[H]
    \centering
    \includegraphics{6pt.eps}
    \caption{6pt.}
    \label{5}
\end{figure}
so the full color ordered amplitude equals to
\begin{align}
    A_1&=\frac{(-1)\asqu{\hat{2}6}\asqu{16}}{\mdavg{25}{56}\!\avg{61}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
    &=\frac{\asqu{26}\avg{16}}{\mdavg{25}{56}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[34]^3}{[4\hat{I}][\hat{I}3]}\notag\\
    &=\frac{\asqu{26}\avg{16}\bcancel{[34]^3}\bcancel{\avg{42}}}{\mdavg{25}{56}\!\mdavg{41}{32}\!\avg{43}\bcancel{[43][43][34]}\bcancel{\avg{24}}}\notag\\
    &=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
\end{align}
where we have used the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the following identities
\begin{equation}
    \cbrak{2\hat{I}}{\hat{I}3}=\cbrak{24}{43}, \qquad \acbrak{4\hat{I}}{\hat{I}1}=\acbrak{43}{\hat{3}1}
\end{equation}
The point here is that we first $\avg{\hat{3}1}$ which does not appear in 5-point case, so we nned to compute it carefully
\begin{gather}
    \text{pole position}: \quad \hat{P_{34}}^2=0=2P_3\cdot P_4=\cbrak{4\hat{3}}{34}\qquad\Rightarrow \qquad \avg{4\hat{3}}=0\notag\\
    \avg{43}+z\avg{42}=0\qquad \Rightarrow \qquad z=-\frac{43}{42}
\end{gather}
then
\begin{align}
    \avg{\hat{3}1}=\avg{31}+z\avg{21}&=\avg{31}-\frac{\avg{43}}{\avg{42}}\avg{21}\notag\\
    &=\frac{\mdavg{42}{31}-\mdavg{43}{21}}{42}\notag\\
    &=\frac{\mdavg{41}{32}}{\avg{42}}
\end{align}
where we have used the Fierz identity
\begin{equation}
    \mdavg{42}{31}+\mdavg{41}{23}+\mdavg{43}{12}=0.
\end{equation}
Simiraly, we can compute the second diagram
\begin{equation}
    A_2=\frac{[\hat{2}5][5\hat{I}]}{[\hat{I}\hat{2}]}\times\frac{1}{s_{25}}\times \frac{(-1)\asqu{16}\asqu{\hat{I}6}}{\mdavg{\hat{I}\hat{3}}{\hat{3}4}
    \!\mdavg{41}{\hat{I}6}\!\avg{61}}
\end{equation}
but from the pole position
\begin{equation}
    \hat{P_{25}}^2=0=2P_2\cdot P_5=\cbrak{52}{\hat{2}5}\qquad\Rightarrow \qquad [\hat{2}5]=0,
\end{equation}
and simiraly
\begin{equation}
    [\hat{2}\hat{I}]=[5\hat{I}]=0.
\end{equation}
Then we can conclude that the left part of the amplitude equals to 0 so $A_2=0$. Finally, we obtain the color-ordered amplitude 
\begin{equation}
    A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=A_1+A_2=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}.
\end{equation}
\subsection{n-point case}
Here, we first propose a compact formula for the color-ordered amplitude
\begin{equation}
    A=\frac{\asqu{2a}\!\asqu{1a}}{\underbrace{\avg{2\star}\cdots \avg{\star 1}}_{SU(N_1)}\underbrace{\avg{2\ast }\cdots \avg{\ast 1}}_{SU(N_2)}}
\end{equation}
where a refer to the particle with - helicity, whichever gauge group it belongs to. And, `$\star$' refers to the ordering for the first gauge group, `$\ast$'
refers to the ordering for the second gauge group. We suppose there are $n_1$ gauge boson 1, $n_2$ gauge boson 2, so the n-point means that $n=n_1+n_2+2$.
\par
The usual way to prove this kind of compact formula is induction. First we suppose that all of the amplitudes with external point lower than n satisfy the compact formula.
